Bioverse: Origins of Life

### 2023-12-16 src/tex/ms.tex
that can't work
add sampling selectivity results and plots

\begin{align}
    P(L|\theta,H_3) & = & f_\mathrm{life} & \text{if } \theta>F_\mathrm{NUV, min}\\
    P(L|\theta,H_3) & = & 0 & \text{otherwise}
\end{align}

@@

>>>>

\begin{align}
    P(L|\theta,H_3) &=  f_\mathrm{life} \quad \text{if } \theta>F_\mathrm{NUV, min}\\
    P(L|\theta,H_3) &=  0               \quad  \text{otherwise}
\end{align}

@@

So far, we have assumed random, uniform distributions of $f_\mathrm{life}$, $F_\mathrm{NUV, min}$, and $F_\mathrm{NUV}$.
A high biosignature detection rate $f_\mathrm{life}$ increases the evidence (cmp. Equation~\ref{eq:bayes_factor}) but we cannot influence it.
The same is true for $F_\mathrm{NUV, min}$, where again higher values increase the evidence as the binomial distribution for $H_\mathrm{3}$ gets increasingly skewed and shifted away from the one for $H_\mathrm{3, null}$.
The distribution of $F_\mathrm{NUV}$ in the planet sample, on the other hand, can be influenced by the survey strategy.
A targeted sampling approach could be to favor extreme values of $F_\mathrm{NUV}$ in the sample selection.
Figure~\ref{fig:semian_selectivity} shows how the probability of obtaining true strong evidence for $H_\mathrm{3}$ scales with selectivity $s$, where $s\in]-1,1[$ such that $F_\mathrm{NUV} \sim Beta(1/10^s,1/10^s)$.
Here, $s=0$ corresponds to a random uniform distribution.
Compared to this case, a high selectivity can increase the probability of obtaining true strong evidence to $\gtrsim \SI{85}{\percent}$ for large samples.

\begin{figure}
    \script{semian_true_evidence.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/semian_selectivity.pdf}
        \caption{Scaling of the probability of obtaining true strong evidence with sample selectivity. Left: Sampling distribution for different selectivity parameters $s$. Right: Resulting \mbox{P(true strong evidence)}. Sampling more extreme values of $F_\mathrm{NUV}$ is more likely to yield strong evidence.}
        \label{fig:semian_selectivity}
    \end{centering}
\end{figure}
